Evaluating Modern vs. Older Buildings: Detailed Analysis on the Apartment Building Evaluation 2023

### 2024-01-22 Output/Paper/Paper1.qmd
Update on reproducable

# load package
library(opendatatoronto)
library(knitr)
library(janitor)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(dplyr)

# read previously cleaned data
bu_eval <-
  read_csv(
    "cleaned_Buildingeval_data.csv",
    show_col_types = FALSE
  )

# read previously created data
data_frequency <-
  read_csv(
    "data_frequency.csv",
    show_col_types = FALSE
  )
```

>>>>

# load package
library(opendatatoronto)
library(knitr)
library(janitor)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(dplyr)
library(readr)

# read previously cleaned data
file_path <- "/cloud/project/Output/Data/cleaned_Buildingeval_data.csv"
bu_eval <- read_csv(file_path, show_col_types = FALSE)

# read previously created data
file_path2 <- "/cloud/project/Output/Data/data_frequency.csv"
data_frequency <-
  read_csv(
    file_path2,
    show_col_types = FALSE
  )
```
